---
title: "World Happiness report"
subtitle: "A Journey through World Happiness:)"
format: html
editor: visual
---

```{r, echo=FALSE, results='hide'}
#| label: load-pkgs
#| message: false
#| warning: false
#| output: false
#| code-fold: true
#| code-summary: "Installed Packages"
### GETTING THE LIBRARIES
if (!require(pacman))
  install.packages(pacman)

pacman::p_load(tidyverse,
               formattable,
               dlookr,
               readxl,
               writexl)
```

## Introduction

"Are you happy?" Despite being a straightforward question, philosophers, artists, and scientists have been captivated by it for millennia. We take a wonderful tour through the World Happiness Report dataset in our quest to discover what makes people truly happy around the world. This proposal describes how we want to investigate and examine this interesting dataset, which runs from 2015 to 2023. This project attempts to solve the puzzles of happiness in a playful and interesting way. Happiness is a universal quest.

## Dataset

### Dataset Description

We are excited to embark on a journey to explore the [World Happiness Report dataset](https://worldhappiness.report/data/), encompassing the years 2015 to 2023. This engaging and illuminating dataset offers a unique glimpse into the factors influencing global happiness and well-being. Let's dive into the details of our chosen dataset:

The World Happiness Report dataset is sourced directly from the official [World Happiness Report website](https://worldhappiness.report/). This esteemed report is published annually by the United Nations, offering insights into the state of happiness and well-being across countries. The dataset is meticulously compiled, verified, and updated each year, making it a reliable source for our analysis.

### Dimensions

The dataset consists of a multidimensional treasure trove of information, including but not limited to:

\- Year: A temporal dimension spanning from 2015 to 2023, allowing us to track changes over time.

\- Country: Covering numerous countries around the world, each providing a unique perspective.

\- Happiness Score: A quantitative measure of happiness, serving as the dependent variable.

\- Economic, Social, and Environmental Indicators: Including GDP per capita, social support, life expectancy, and more.

\- Freedom, Corruption, and Generosity Metrics: Providing insights into the cultural and governance aspects influencing happiness.

\- Dystopia Residual: A reference point for low happiness, helping us gauge relative happiness scores.

### Reason for Choosing this Dataset

The World Happiness Report dataset offers a perfect blend of intriguing questions and meaningful insights. By exploring this dataset, we aim to understand the factors that contribute to happiness and well-being across diverse societies. Furthermore, we chose this dataset for the following reasons:

1\. Global Relevance: Happiness is a fundamental aspect of human well-being, and this dataset provides a unique perspective on happiness trends worldwide. Our analysis can offer insights into what makes societies and individuals happy, transcending borders and cultures.

2\. Temporal Insights: The dataset covers a wide range of years, enabling us to track happiness trends and identify potential causative factors over time. This temporal dimension adds depth to our analysis.

```{r, echo=TRUE, results='hide'}
#| label: load-dataset
#| message: false

```

## Questions

1.  How do various factors contribute to the overall happiness score across different countries over the years?

## Analysis plan

-   **Approach for Question 1**

    The different factors involved are as follows : economy ("GDP per capita"), family ("social support"), health("healthy life expectancy at birth"), freedom ("freedom to make life choices"), trust("perceptions of corruption") and genorosity ("genorosity").

    To explore how various factors contribute to the overall happiness score across different countries over the years, we have designed an interactive analysis where users can select a specific year and country from drop-down menus, allowing for a dynamic and personalized exploration of the data. We are planning to create a bar chart where the x-axis represents the factors (independent variables), and the y-axis represents their contribution to the overall happiness score. For better visulaization we are planning to choose a Grouped Bar chart, where separate bars represents each factor, and their heights represent their contributions to the overall happiness score. This chart provides a side-by-side comparison of each factor's contribution. We are planning to expand the analysis by incorporating a stacked bar plot to gain more comprehensive visualization.

## Plan of Attack

#### Week 1: (Oct 16 - Oct 22) \[Everyone\]

#### *Data Selection and Initial Planning*

-   *Tasks:*
    -   Identify and download the World Happiness Report dataset.
    -   Clean and preprocess the data, removing any inconsistencies or missing values.
    -   Familiarizing with the dataset's structure and variables.
    -   Analysing more on the specific questions we want to address and the visualizations.
    -   Begin designing a rough sketch of the shiny app's layout.

#### Week 2: (Oct 23 - Oct 29)\[Everyone\]

#### *Proposal Writing*

-   *Tasks:*
    -   Write a project proposal that includes the project's goals, objectives, and scope.
    -   Define the questions you aim to answer with the shiny application.
    -   Outline the design and interactivity features we plan to include.
    -   Create a project timeline with specific milestones.

#### Week 3: (Oct 30 - Nov 5) \[Everyone\]

#### *Data Exploration and Visualization Planning*

-   *Tasks:*
    -   Conduct exploratory data analysis (EDA) to understand the dataset better.
    -   Identify interesting patterns, correlations, or outliers in the data.
    -   Sketch initial ideas for the app's layout and visualizations.

#### Week 4: (Nov 6 - Nov 12) \[Everyone\]

#### *Shiny Application Layout Designing*

-   *Tasks:*
    -   Select the tools and libraries to be used for creating the app.
    -   Plan the layout, including the placement of plots, widgets, and navigation.
    -   Create a wireframe for user interface.

#### Week 5: (Nov 13 - Nov 19) \[TBD\]

#### *Plot Creation*

-   *Tasks:*
    -   Develop the plots and interactive components.
    -   Ensure that the plots represent the data accurately and are visually appealing.
    -   Initial integration of interactive elements into the shiny app.

#### Week 6: (Nov 20 - Nov 26) \[TBD\]

#### *Shiny App Development and Refinement*

-   *Tasks:*
    -   Code the functionality of the app using Shiny's reactive elements.
    -   Implement interactivity features like dropdowns and filters.
    -   Test the app's performance and user experience.

#### Week 7: (Nov 27 - Dec 3) \[Everyone\]

#### *Testing and Modifications*

-   *Tasks:*
    -   Conduct testing to identify and fix any bugs or issues.
    -   Gather feedback.
    -   Make improvements based on the feedback received.

#### Week 8: (Dec 4 - Dec11) \[Everyone\]

#### *Finalization and Presentation*

-   *Tasks:*
    -   Make any final refinements to the application.
    -   Complete the write-up or documentation.
    -   Prepare a presentation for the project.
